---
output: html_fragment
---

# About traceShiny

This is build with trace v1.0.0

# Citation

If you used traceShiny for your research, please use the following citation: [Jiang, A., Correia, K., Gillis, T., Oliver, E. L., Jones, B. P., McAllister, B., Mejia Maza, A., MacDonald, M. E., Mouro Pinto, R., Wheeler, V. C., Gusella, J. F., & McLean, Z. L. (2026). TRACE: Open-source software for quantifying somatic variation of tandem repeats by capillary electrophoresis. Journal of Huntington's disease, 18796397261448958. Advance online publication.](https://journals.sagepub.com/doi/10.1177/18796397261448958)

```{r, include=FALSE}
#TOODO
# add publication link


```

# Contact Us

traceShiny was designed and maintained by Andrew Jiang and Zachariah McLean based at the Center for Genomic Medicine at Massachusetts General Hospital and Harvard Medical School.

Please forward any queries to [Andrew Jiang](mailto:ajiang8@mgh.harvard.edu) or log an issue at the [Github page](https://github.com/zachariahmclean/traceShiny/issues).

```{r, include=FALSE}
#TOODO



```
